Template for Grading Scientific Computing Software

### 2020-04-15 StateOfPractice/Peter-Notes/GradingTemplate.tex
comments on old template

\begin{longtable}{p{16cm}}
  \caption{Grading Template}   \label{table:TemplateFull}\\
  \toprule
  \textbf{Summary Information}\\
  \midrule
  Software name? (string)\\
  URL? (url)\\
  Educational institution (string)\\
  Software purpose (string)\\
Number of developers (number)\ad{It might be hard to decide. For example 3D
Slicer has 171 people with commits to its repo, but on its website, 18
contributors(including people who are not developers) are acknowledged.}\\
  How is the project funded (string)\\
  Number of downloads for current version (number)\\
  Release date (date)\\
  Last updated (date)\\
  Status (\{alive, dead, unclear\})\\
  License (\{GNU GPL, BSD, MIT, terms of use, trial, none, unclear\})\\
  Platforms (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Category (\{concept, public, private\})\\
  Development model (\{open source, freeware, commercial\})\\
  Publications using the software (set of url)\\
  Publications about the software (set of url) \\
Is source code available? (\{yes, no\})\ad{It might be better to directly ask
for a set of url, and the answer can be n/a if it's not open source, or unclear
if it can't be determined. An example is as follows.}\\
  \ad{Example}Source code URL (\{set of url, n/a, unclear\})\\
  Programming language(s) (set of \{FORTRAN, Matlab, C, \CC, Java, R, Ruby,
  Python, Cython, BASIC, Pascal, IDL, unclear\})\\

  \midrule
  \textbf{Installability} (Measured via installation on a virtual machine.)\\
  \midrule

  Are there installation instructions? (\{yes, no\})\\
  Are the installation instructions linear? (\{yes, no, n/a\})\\
  Is there something in place to automate the installation? (\{yes$^*$, no\})\\
Is there a specified way to validate the installation, such as a test suite?
\ad{What's the difference between this one and the getting started tutorial?}
(\{yes$^*$, no\})\\
How many steps were involved in the installation? (number) \ad{what if the
installation has different steps on different OS?}\\
How many software packages need to be installed before or during
installation?(number) \ad{should it be 0 if no packages needed? I saw some
answers with "no"
or "none"}\\
Run uninstall, if available. Were any obvious problems caused? (\{unavail,
yes$^*$, no\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Are external libraries used? (\{yes$^*$, no, unclear\})\\
  Does the community have confidence in this library? (\{yes, no, unclear\})\\
  Any reference to the requirements specifications of the program?
(\{yes$^*$, no, unclear\})\ad{Seems like a good question to put in the
questionnaire}\\
What tools or techniques are used to build confidence of correctness?
(string)\ad{Seems like a good question to put in the questionnaire}\\
If there is a getting started tutorial, is the output as expected? (\{yes,
no$^*$, n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Did the software ``break'' during installation? (\{yes$^*$, no\})\\
Did the software ``break'' during the initial tutorial testing? (\{yes$^*$, no,
n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

Does the software handle garbage input reasonably? (\{yes, no$^*$\}) \ad{How do
we prepare garbage input?}\\
  For any plain text input files, if all new lines are replaced with new lines
  and carriage returns, will the software handle this gracefully? (\{yes,
  no$^*$, n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is there evidence that performance was considered? (\{yes$^*$, no\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is there a getting started tutorial? (\{yes, no\})\\
  Is there a standard example that is explained? (\{yes, no\})\\
  Is there a user manual? (\{yes, no\})\\
  Does the application have the usual ``look and feel'' for the platform it is
  on? (\{yes, no$^*$\})\\
  Are there any features that show a lack of visibility? (\{yes, no$^*$\})\\
  Are expected user characteristics documented? (\{yes, no\})\\
What is the user support model? (string)\ad{Can GitHub be one? Many users
directly ask questions there by open new issues.}\\
  Overall impression? (\{1 .. 10\})\\

@@

Is there a history of multiple versions of the software? (\{yes, no,
unclear\})\\
  Is there any information on how code is reviewed, or how to contribute?
  (\{yes$^*$, no\})\\
  Is there a changelog?  (\{yes, no\})\\
What is the maintenance type? (set of \{corrective, adaptive, perfective,
unclear\})\\
  What issue tracking tool is employed? (set of \{Trac, JIRA, Redmine, e-mail,
discussion board, sourceforge, google code, git, none, unclear\}) \ad{Does git
mean GitHub and GitLab? Should we add BitBucket here?}\\
Are the majority of identified bugs fixed? (\{yes, no$^*$, unclear\})\ad{It
might be better to record a number here. An example is as follows.}\\
\ad{Example}What is the percentage of identified issues that are closed?
(percentage)\\
Which version control system is in use? (\{svn, cvs, git, github, unclear\})\\
Is there evidence that maintainability was considered in the design?
  (\{yes$^*$, no\})\\
Are there code clones? (\{yes$^*$, no, unclear\})\ad{Might need to test some
static analyzer.}\\
  Overall impression? (\{1 .. 10\})\\

@@

Are any portions of the software used by another package? (\{yes$^*$,
no\})\ad{It seems hard to find an answer for some software.}\\
  Is there evidence that reusability was considered in the design? (API
documented, web service, command line tools, ...) (\{yes$^*$, no, unclear\})\\
Overall impression? (\{1 .. 10\})\\

@@

  What platforms is the software advertised to work on?
  (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Are special steps taken in the source code to handle portability? (\{yes$^*$,
  no, n/a\}) \\
  Is portability explicitly identified as NOT being important? (\{yes, no\})\\
Convincing evidence that portability has been achieved? (\{yes$^*$,
no\})\ad{Seems like a good question to put in the questionnaire}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Consistent indentation and formatting style? (\{yes, no, n/a\})\\
  Explicit identification of a coding standard? (\{yes$^*$, no, n/a\})\\
  Are the code identifiers consistent, distinctive, and
  meaningful? (\{yes, no$^*$, n/a\})\\
Are constants (other than 0 and 1) hard coded into the program? (\{yes, no$^*$,
n/a\})\\
Comments are clear, indicate what is being done, not how? (\{yes, no$^*$,
n/a\})\\
  Is the name/URL of any algorithms used mentioned?
  (\{yes, no$^*$, n/a\})\\
  Parameters are in the same order for all functions? (\{yes, no$^*$, n/a\})\\
  Is code modularized? (\{yes, no$^*$, n/a\})\\
  Descriptive names of source code files? (\{yes, no$^*$, n/a\})\\
Is a design document provided? (\{yes$^*$, no, n/a\})\ad{What is a design
document? There can be some examples.}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Does the software interoperate with external systems? (\{yes$^*$, no\})\\
  Is there a workflow that uses other softwares? (\{yes$^*$, no\})\\
If there are external interactions, is the API clearly defined? (\{yes$^*$, no,
n/a\})\\
  \ad{Some more suggested questions are as follows:}\\
  \ad{1.}Can the output be used by other software as input?(\{yes$^*$, no\})\\
  \ad{2.}Can it take output from other software as input?(\{yes$^*$, no\})\\
\ad{3.}Does the software generate output files with uncommon formats or
extensions? Such as the ones that can only be used by itself.(\{yes$^*$, no,
n/a\})\\
  \ad{4.}Can the software work with customized plug-ins? (\{yes, no\})\\
  Overall impression? (\{1 .. 10\})\\

@@

Is the development process defined? If yes, what process is used. (\{yes$^*$,
no, n/a\})\ad{Seems like a good question to put in the questionnaire}\\
  Ease of external examination relative to other products
  considered?  (\{1 .. 10\})\\
  \ad{Some more suggested questions are as follows:}\\
\ad{1.}Are there any documents recording the development process and status?
(\{yes$^*$, no,\})\\
  \ad{2.}Are there release notes? (\{yes, no\})\\
\ad{3.}In the issue tracking system, are there at least some issues assigned to
specific developers? (\{yes, no\})\ad{It would be better to get a percentage,
but the empirical tool can't achieve this. It might be worth to manually count
the most recent 50 issues.}\\
\ad{4.}In the issue tracking system, are there at least some issues with tags of 
types and priorities? (\{yes, no\})\ad{In GitHub, tags are optional. In
BitBucket, it seems to be mandatory. In SourceForge, it seems to be not
supported.}\\
\ad{5.}Are there any project management tools used during the
development?\ad{Seems like a good question to put in the questionnaire}\\
  Overall impression? (\{1 .. 10\})\\

>>>>

\begin{longtable}{p{16cm}}
  \caption{Grading Template}   \label{table:TemplateFull}\\
  \toprule
  \textbf{Summary Information}\\
  \midrule
  Software name? (string)\\
  URL? (url)\\
  Educational institution (string)\\
  Software purpose (string)\\
Number of developers (number)\\
  How is the project funded (string)\\
  Number of downloads for current version (number)\\
  Release date (date)\\
  Last updated (date)\\
  Status (\{alive, dead, unclear\})\\
  License (\{GNU GPL, BSD, MIT, terms of use, trial, none, unclear\})\\
  Platforms (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  Category (\{concept, public, private\})\\
  Development model (\{open source, freeware, commercial\})\\
  Publications using the software (set of url)\\
  Publications about the software (set of url) \\
  Is source code available? (\{yes, no\})\\
  Source code URL (\{set of url, n/a, unclear\})\\
  Programming language(s) (set of \{FORTRAN, Matlab, C, \CC, Java, R, Ruby,
  Python, Cython, BASIC, Pascal, IDL, unclear\})\\

  \midrule
  \textbf{Installability} (Measured via installation on a virtual machine.)\\
  \midrule
 \pmi{Are required (known to work) operating system versions listed?}\\
  Are there installation instructions? (\{yes, no\})\\
  Are the installation instructions linear? (\{yes, no, n/a\})\\
  Is there something in place to automate the installation? (\{yes$^*$, no\})\\
Is there a specified way to validate the installation, such as a test suite?
(\{yes$^*$, no\})\\
How many steps were involved in the installation? (number) \\
How many software packages need to be installed before or during
installation?(number) \\
\pmi{are specific versions of required packages listed?}\\
\pmi{are there links to or instructions for the installation of required packages?}\\
Run uninstall, if available. Were any obvious problems caused? (\{unavail,
yes$^*$, no\})\\
\pmi{In your opinion could a non-developer of the software effectively install this software by verbatim following the instructions}\\
\pmi{Was troubleshooting the instructions necessary to install the system?}
  Overall impression? (\{1 .. 10\})\\

@@

  Are external libraries used? (\{yes$^*$, no, unclear\})\\
  \pmi{are versions of external libraries specified?}\\
  \pmi{are instructions for finding/installing the external libraries specified?}\\
  Does the community have confidence in this library? (\{yes, no, unclear\})\\
  Any reference to the requirements specifications of the program?
(\{yes$^*$, no, unclear\})\\
What tools or techniques are used to build confidence of correctness?
(string)\\
If there is a getting started tutorial, is the output as expected? (\{yes,
no$^*$, n/a\})\\
\pmi{Does the getting started tutorial provide an answer to verify against?}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Did the software ``break'' during installation? (\{yes$^*$, no\})\\
  \pmi{was a helpful error message provided?}
    \pmi{was the installation recoverable?}
Did the software ``break'' during the initial tutorial testing? (\{yes$^*$, no,
n/a\})\\
  \pmi{was a helpful error message provided?}\\
  \pmi{was the testing recoverable?}\\
  Overall impression? (\{1 .. 10\})\\

@@

Does the software handle garbage input reasonably? (\{yes, no$^*$\}) \\
  For any plain text input files, if all new lines are replaced with new lines
  and carriage returns, will the software handle this gracefully? (\{yes,
  no$^*$, n/a\})\\
  \pmi{Does the system react gracefully when required libraries or input files are not provided? Descriptive message?}
  Overall impression? (\{1 .. 10\})\\

@@

  Is there evidence that performance was considered? (\{yes$^*$, no\})\\
  \pmi{Does the software (optionally) use GPU for processing?}\\
  Overall impression? (\{1 .. 10\})\\

@@

  Is there a getting started tutorial? (\{yes, no\})\\
  Is there a standard example that is explained? (\{yes, no\})\\
  \pmi{Is a solution provided?}\\
  Is there a user manual? (\{yes, no\})\\
  Does the application have the usual ``look and feel'' for the platform it is
  on? (\{yes, no$^*$\})\\
  \pmi{this question is vague to me}\\
  Are there any features that show a lack of visibility? (\{yes, no$^*$\})\\
  Are expected user characteristics documented? (\{yes, no\})\\
What is the user support model? (string)\\
  Overall impression? (\{1 .. 10\})\\

@@

Is there a history of multiple versions of the software? (\{yes, no,
unclear\})\\
  Is there any information on how code is reviewed, or how to contribute?
  (\{yes$^*$, no\})\\
  Is there a changelog?  (\{yes, no\})\\
What is the maintenance type? (set of \{corrective, adaptive, perfective,
unclear\})\\
  What issue tracking tool is employed? (set of \{Trac, JIRA, Redmine, e-mail,
discussion board, sourceforge, google code, git, none, unclear\})\\
Are the majority of identified bugs fixed? (\{yes, no$^*$, unclear\})\\
What is the percentage of identified issues that are closed?
(percentage)\\
\pmi{is there a way to measure average time to close issues?}\\
\pmi{are files well commented? - percentage?}\\
\pmi{comment on module / file size}\\
Which version control system is in use? (\{svn, cvs, git, github, unclear\})\\
Is there evidence that maintainability was considered in the design?
  (\{yes$^*$, no\})\\
Are there code clones? (\{yes$^*$, no, unclear\})\\
  Overall impression? (\{1 .. 10\})\\

@@

Are any portions of the software used by another package? (\{yes$^*$,
no\})\\
  Is there evidence that reusability was considered in the design? (API
documented, web service, command line tools, ...) (\{yes$^*$, no, unclear\})\\
\pmi{Are module interfaces clearly defined?}\\
\pmi{Are modules described in the user guide?}\\
\pmi{Is the system modularized?}\\
Overall impression? (\{1 .. 10\})\\

@@

  What platforms is the software advertised to work on?
  (set of \{Windows, Linux, OS X, Android, Other OS\})\\
  \pmi{What versions of these platforms is the software advertised to work on?}\\
  \pmi{How many external libraries are needed?}\\
  Are special steps taken in the source code to handle portability? (\{yes$^*$,
  no, n/a\}) \\
  Is portability explicitly identified as NOT being important? (\{yes, no\})\\
Convincing evidence that portability has been achieved? (\{yes$^*$,
no\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Consistent indentation and formatting style? (\{yes, no, n/a\})\\
  Explicit identification of a coding standard? (\{yes$^*$, no, n/a\})\\
  Are the code identifiers consistent, distinctive, and
  meaningful? (\{yes, no$^*$, n/a\})\\
Are constants (other than 0 and 1) hard coded into the program? (\{yes, no$^*$,
n/a\})\\
Comments are clear, indicate what is being done, not how? (\{yes, no$^*$,
n/a\})\\
  Is the name/URL of any algorithms used mentioned?
  (\{yes, no$^*$, n/a\})\\
  Parameters are in the same order for all functions? (\{yes, no$^*$, n/a\})\\
  Is code modularized? (\{yes, no$^*$, n/a\})\\
  Descriptive names of source code files? (\{yes, no$^*$, n/a\})\\
Is a design document provided? (\{yes$^*$, no, n/a\})\\
  Overall impression? (\{1 .. 10\})\\

@@

  Does the software interoperate with external systems? (\{yes$^*$, no\})\\
  Is there a workflow that uses other softwares? (\{yes$^*$, no\})\\
If there are external interactions, is the API clearly defined? (\{yes$^*$, no,
n/a\})\\

@@

Is the development process defined? If yes, what process is used. (\{yes$^*$,
no, n/a\})\\
  Ease of external examination relative to other products
  considered?  (\{1 .. 10\})\\
  Overall impression? (\{1 .. 10\})\\

### 2020-04-15 StateOfPractice/Peter-Notes/TemplateToGradeSCSoft_Comments.tex
comments on old template

\documentclass[letterpaper,cleveref]{lipics-v2019}

\usepackage{natbib}
\usepackage{booktabs}
\usepackage{amsmath,amsthm}
\usepackage{hyperref}

\usepackage{hyperref}
\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

@@

\newcommand{\notdone}[1]{\textcolor{red}{#1}}
\newcommand{\done}[1]{\textcolor{black}{#1}}

%\oddsidemargin 0mm
%\evensidemargin 0mm
%\textwidth 160mm
%\textheight 200mm

\theoremstyle{definition}
\newtheorem{defn}{Definition}

\title{Methodology for Assessing the State of the Practice for Domain X} 
\author{Spencer Smith}{McMaster University, Canada}{smiths@mcmaster.ca}{}{}
\author{Jacques Carette}{McMaster University, Canada}{carette@mcmaster.ca}{}{}
\author{Olu Owojaiye}{McMaster University, Canada}{owojaiyo@mcmaster.ca}{}{}
\author{Peter Michalski}{McMaster University, Canada}{michap@mcmaster.ca}{}{}
\author{Ao Dong}{McMaster University, Canada}{donga9@mcmaster.ca}{}{}

\authorrunning{Smith et al.}  \Copyright{Spencer Smith and Jacques Carette and
Olu Owojaiye and Peter Michalski and Ao Dong}

\date{\today}

\hideLIPIcs
\nolinenumbers

\begin{document}
\maketitle

\begin{abstract}
	...
\end{abstract}

\tableofcontents

\section{Introduction} \label{SecIntroduction}

Purpose and scope of the document.  \wss{Needs to be filled in.  Should
	reference the overall research proposal, and the ``state of the practice''
	exercise in particular.}

\section{Overview of Steps in Assessing Quality of the Domain Software}

\begin{enumerate}
\item Identify domain.  (Provide criteria on a candidate domain.)
\item 
\end{enumerate}

\section{Identify Candidate Software}

\begin{enumerate}
	\item Must be open source.
	\item Must have GitHub repository.
\end{enumerate}

\section{Domain Analysis} \label{SecDomainAnalysis}

Commonality analysis.  Follow as for mesh generator (likely with less detail).

Commonality analysis document Steps:
\begin{enumerate}
	\item Introduction
	\item Overview of Domain
	\item Add Commonalities - Split into simulation, input, output, and nonfunctional requirements
	\item Add Variabilites - Split into simulation, input, output, system constraints, and nonfunctional requirements
	\item Add Parameters of Variation - Split into simulation, input, output, system constraints, and nonfunctional requirements
	\item Add Terminology, Definitions, Acronyms
\end{enumerate}

Commonality analysis for Lattice Boltzmann Solvers can be found \href{run:../Peter-Notes/Commonality-Analysis-LB-Systems.pdf}{here}.

\section{Empirical Measures}

\subsection{Raw Data}
Measures that can be extracted from on-line repos.

\ad{Still at brainstorm stage.}
\begin{itemize}
\item number of contributors
\item number of watches
\item number of stars
\item number of forks
\item number of clones
\item number of commits
\item number of total/code/document files
\item lines of total/logical/comment code
\item lines/pages of documents (can pdf be extracted?)
\item number of total/open/closed/merged pull requests
\item number of total/open/closed issues
\item number of total/open/closed issues with assignees
\end{itemize}

Instead of only focus on the current status of the above numbers, we may find
the time history of them to be more valuable. For example, the number of
contributors over time, the number of lines of code over time, the number of
open issues over time, etc.

\subsection{Processed Data}
Metrics that can be calculated from the raw data.

\ad{Still at brainstorm stage.}
\begin{itemize}
\item percentage of total/open/closed issues with assignees -
Visibility/Transparency
\item lines of new code produced per person-month - Productivity
\item lines/pages of new documents produced per person-month - Productivity
\item number of issues closed per person-month - Productivity
\item percentage of comment lines in the code - maintainability \ad{Not Ao's
qualities}
\end{itemize}

In the above calculations, a month can be determined to be 30 days.

\subsection{Tool Tests}
\ad{This section is currently a note of unorganized contents. Most parts will beremoved or relocated.}

\ad{This citation needs to be deleted later. It's here because my compiler
doesn't work with 0 citations}
\cite{Emms2019}

Most tests were done targeting to the repo of 3D Slicer
\href{https://github.com/tomgi/git_stats}{GitHub repo}

\subsubsection{git-stats}
\href{https://github.com/tomgi/git_stats}{GitHub repo}

Test results:
\href{http://git-stats-slicer.ao9.io/}{http://git-stats-slicer.ao9.io/} the
results are output as webpages, so I hosted for you to check. Data can be
downloaded as spreadsheets.

\subsubsection{git-of-theseus}
\href{https://github.com/erikbern/git-of-theseus}{GitHub repo}

Test results: It took about 100 minutes for one repo on a 8 core 16G ram Linux
machine. It only outputs graphs.

\subsubsection{hercules}
\href{https://github.com/src-d/hercules}{GitHub repo}

Test results: this one seems to be promising, but the installation is
complicated with various errors.

\subsubsection{git-repo-analysis}
\href{https://github.com/larsxschneider/git-repo-analysis}{GitHub repo}

\subsubsection{HubListener}
\href{https://github.com/pjmc-oliveira/HubListener}{GitHub repo}

The data that HubListener can extract.

Raw:
\begin{itemize}
\item Number of Files
\item Number of Lines
\item Number of Logical Lines
\item Number of Comments
\end{itemize}

Cyclomatic:
\href{https://www.geeksforgeeks.org/cyclomatic-complexity/}{Intro}
\begin{itemize}
\item Cyclomatic Complexity
\end{itemize}

Halstead:
\href{https://www.geeksforgeeks.org/software-engineering-halsteads-software-metrics/}{Intro}
\begin{itemize}
\item Halstead Effort
\item Halstead Bugs
\item Halstead Length
\item Halstead Difficulty
\item Halstead Time
\item Halstead Vocabulary
\item Halstead Volume
\end{itemize}

Test results: HubListener works well on the repo of itself, but it did not work
well on some other repos.

\subsubsection{gitinspector}
\href{https://github.com/ejwa/gitinspector}{GitHub repo}

Test results: it doesn't work well. Instead of creating output results, it
prints the results directly in the console.

\section{User Experiments}

Describe experiments with users to assess usability, performance etc.

\section{Analytic Hierarchy Process}

Describe process.  Domain expert review.

\section{Quality Specific Measures}

\subsection{\notdone{Installability} \oo{owner}}

\subsection{\notdone{Correctness} \oo{owner}}

\subsection{\notdone{Verifiability/Testability} \oo{owner}}

\subsection{\notdone{Validatability} \oo{owner}}

\subsection{\notdone{Reliability} \oo{owner}}

\subsection{\notdone{Robustness} \pmi{owner}}

\subsection{\notdone{Performance} \pmi{owner}}

\subsection{\notdone{Usability} \jc{owner}}

\subsection{\notdone{Maintainability} \pmi{owner}}

\subsection{\notdone{Reusability} \pmi{owner}}

\subsection{\notdone{Portability} \pmi{owner}}

\subsection{\notdone{Understandability} \jc{owner}}

\subsection{\notdone{Interoperability} \ad{owner}}

\subsection{\notdone{Visibility/Transparency} \ad{owner}}

\subsection{\notdone{Reproducibility} \wss{owner}}

\subsection{\notdone{Productivity} \ad{owner}}

\subsection{\notdone{Sustainability} \wss{owner}}

\subsection{\notdone{Completeness} \ad{owner}}

\subsection{\notdone{Consistency} \ad{owner}}

\subsection{\notdone{Modifiability} \jc{owner}}

\subsection{\notdone{Traceability} \jc{owner}}

\subsection{\notdone{Unambiguity} \wss{owner}}

\subsection{\notdone{Verifiability} \wss{owner}}

\subsection{\notdone{Abstract} \wss{owner}}

\section{Using Data to Rank Family Members}

Describe AHP process (or similar).

\newpage

\bibliographystyle {plainnat}
\bibliography {../../CommonFiles/ResearchProposal}

>>>>

\documentclass[12pt]{article}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xspace}
\usepackage{fullpage}
\usepackage{hyperref}

\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=red,          % color of internal links (change box color with
%linkbordercolor)
citecolor=blue,       % color of links to bibliography
filecolor=magenta,   % color of file links
urlcolor=cyan           % color of external links
}

@@

\def\CC{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}\xspace}

\begin{document}

\title{Template for Grading Scientific Computing Software} 
\author{Spencer Smith, Adam Lazzarato, Yue Sun, Zheng Zeng,\\ Vasudha Kapil and Jacques Carette}
\date{\today}

\maketitle
\include{GradingTemplate}
